Visualising 3D structures

### 2022-03-23 analysis/ThreeDStructure.Rmd
add missing files
workflowr::wflow_publish(files = "analysis/ThreeDStructure.Rmd")

```{r}
ara_SOS3_gaps <- gap.inspect(ara_SOS3_real$xyz)
ara.xyz <- ara_SOS3_real$xyz[ara_SOS3_gaps$f.inds]

amphi_gaps <- gap.inspect(amphibolis_SOS3_alpha$xyz)
amph.xyz <- amphibolis_SOS3_alpha$xyz[amphi_gaps$f.inds]

a <- torsion.xyz(ara.xyz, atm.inc=1)
b <- torsion.xyz(amph.xyz, atm.inc=1)
d.ab <- wrap.tor(a-b)
d.ab[is.na(d.ab)] <- 0
plot.bio3d(abs(d.ab), typ="h", xlab="Residue No.", 
           ylab = "Difference Angle")

```
```{r}
posi_SOS3_gaphs <- gap.inspect(posi_SOS3_alpha$xyz)
posi.xyz <- posi_SOS3_alpha$xyz[posi_SOS3_gaphs$f.inds]

a <- torsion.xyz(posi.xyz, atm.inc=1)
b <- torsion.xyz(amph.xyz, atm.inc=1)
d.ab <- wrap.tor(a-b)
d.ab[is.na(d.ab)] <- 0
plot.bio3d(abs(d.ab), typ="h", xlab="Residue No.", 
           ylab = "Difference Angle")

@@

>>>>

@@

OK cool - now we can align all proteins and make proper plots!
